### 2014-03-31 paper/relatedwork.tex
notes from tovi
paper work, adding tovi comments

@@

Previous work has investigated the integration of interactivity with the fabrication process.  Printed Optics (\cite{Willis-printedoptics}) used light pipes, solid clear tubes, to create integrated displays: our work is inspired by this and goes towards a design tool for these capabilities; Printed Optics is a part of our design space, which includes other uses of pipes.  Willis, et al., also did not offer a design tool or techniques for creating light pipes automatically.  Sauron investigated the use of computer vision to track interactions with physical mechanisms \cite{Savage-sauron}.  While Savage, et al., used mirrors for redirection, we believe that the required line-of-sight operation for their computer vision techniques may be possible using printed optics or inserted optical fibers.  Slyper, et al., \cite{Slyper-pressure} 3D printed flexible robot armatures capable of sensing interaction via changes in air pressure.  This technique is complementary to ours, as we allow for placing these interactive elements anywhere on an object's surface while they had to place them in locations accessible for electronics insertion.  General-purpose routing for connecting 2D capacitive sensors to terminals is discussed in Midas \cite{Savage-midas}.  This technique, based on circuitboard routing, are limited to planar and unfoldable shapes, and are intended for use on the surface of objects rather than through their cores.  Acoustic Barcodes explored integrating ridges into digitally fabricated objects, whose acoustic signatures when scraped provided an ID code \cite{Harrison-acoustic}.  Fabrickation works towards rapid fabrication of functional objects by integrating construction kit building blocks \cite{Mueller-fabrickation}.

@@

Prior work on modeling the interior of objects (as opposed to their exterior) has been limited.  In Make it Stand, material is removed from the interior of objects with the goal of changing their center of gravity \cite{Prevost-makeitstand}.  Bickel, et al., explored enforcing deformation behavior with material blending \cite{Bickel-deformation}, while B\"{a}cher, et al., built an algorithm for automatically placing 3D fabricatable joints into meshes \cite{Bacher-articulated}.  Sauron automatically modified the interior of existing mechanical objects to make them amenable to vision-based sensing \cite{Savage-sauron}, and Infrastructs created encoded interior cavities in 3D printed objects designed to be sensed with a terahertz imaging tool.  Our work differs in that we want to allow users to design pipes and integrate interactive objects with them.

>>>>

\tovi{make sure to have mini intros and conclusions for each subsection.  it's ok to discuss several papers at once if they are similar.  each paper needs a sentence to say what distinguishes us from it}

@@

Previous work has investigated the integration of interactivity with the fabrication process.  Printed Optics (\cite{Willis-printedoptics}) used light pipes, solid clear tubes, to create integrated displays: our work is inspired by this and goes towards a design tool for these capabilities; Printed Optics is a part of our design space, which includes other uses of pipes.  Willis, et al., also did not offer a design tool or techniques for creating light pipes automatically.  Slyper, et al., in \cite{Slyper-pressure} 3D printed flexible robot armatures capable of sensing interaction via changes in air pressure.  This technique is complementary to ours, as we allow for placing these interactive elements anywhere on an object's surface while they had to place them in locations accessible for electronics insertion. Acoustic Barcodes explored integrating ridges into digitally fabricated objects, whose acoustic signatures when scraped provided an ID code \cite{Harrison-acoustic}; while pipes can be used for identification and to create aural feedback, this is not our only goal.   Sauron investigated the use of computer vision to track interactions with physical mechanisms \cite{Savage-sauron}.  While Savage, et al., used mirrors for redirection, we believe that the required line-of-sight operation for their computer vision techniques may be possible using printed optics or inserted optical fibers.  General-purpose routing for connecting 2D capacitive sensors to terminals is discussed in Midas \cite{Savage-midas}.  This technique, based on circuitboard routing, are limited to planar and unfoldable shapes, and are intended for use on the surface of objects rather than through their cores.  Fabrickation works towards rapid fabrication of functional objects by integrating construction kit building blocks \cite{Mueller-fabrickation}.  While we recognize that 3D printing requires a significant amount of time, we believe that creating precise internal structures in 3D printed objects is a strong case for digital fabrication over manual assembly or traditional methods.

@@

Prior work on modeling the interior of objects (as opposed to their exterior) has been limited.  In Make it Stand, material is removed from the interior of objects with the goal of changing their center of gravity \cite{Prevost-makeitstand}.  The creation of such hollow chambers is a part of our design space, however our contribution is orthogonal as we do not focus on re-balancing objects using these chambers.  Bickel, et al., explored enforcing deformation behavior with material blending \cite{Bickel-deformation}, while B\"{a}cher, et al., built an algorithm for automatically placing 3D fabricatable joints into meshes \cite{Bacher-articulated}.  Our focus is not on articulated or deformable 3D prints, although we do perform interior modeling.  Takayama, et al., built a system described in \cite{Takayama-fruit} which allowed users to create internal color maps of the interior of objects, allowing them to see ``slices'' of their ``oranges.''  This differs from our contribution, as our pipes are designed for fabrication, and focus on function rather than appearance.  Sauron automatically modified the interior of existing mechanical objects to make them amenable to vision-based sensing \cite{Savage-sauron}, and Infrastructs created encoded interior cavities in 3D printed objects designed to be sensed with a terahertz imaging tool.  Our work differs in that we want to allow users to design pipes and integrate interactive objects with them.
